Efficient Coalition Formation for Web Services

### 2013-03-09 papers/coalition/coalition.tex
Changes

In this section we discuss the parameters and preliminary concepts that we use in the rest of paper. The way communities of web services are structured and engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

\subsection{The Architecture and Entities }
\subsubsection{Web Services}
\subsubsection{Master Web Service of Communities}
\subsubsection{Users}

\subsection{Task Parameters}
\subsubsection{Request rate}
\subsubsection{Consumption}
\subsubsection{Requested Reponse Time}
\subsubsection{Requested Availability}
\subsubsection{Requested Success Rate}

\subsection{Web Sercive Parameters}
\subsubsection{Throughput}
\subsubsection{Capacity}
\subsubsection{Cost}
\subsubsection{Reponse Time}
\subsubsection{Availability}
\subsubsection{Reliability}
\subsubsection{Success Rate}
\subsubsection{Reputation}

@@

In figure \ref{performancemany} we compare our \emph{Web Services and many Communities} scenario with a method which ignores QoS parameters and forms coalitions and allow web services to join only if they have enough requests for them in other words web services can join a community when request rate is less that throughput of all web services inside community ignoring QoS parameters. We name this method \emph{Normal method} and use it as our benchmark for our QoS aware coalition formation process. As results illustrate clearly, our QoS aware method, forms better coalitions of web services improving performance and satisfaction for both web service and coalitions.

>>>>

In this section we discuss the parameters and preliminary concepts that we use in the rest of paper.

\subsection{The Architecture}

Our system consists of three main type of entities working together:

\emph{1) Web services} are rational entities providing services to end users. They aim to maximize their individual income by receiving enough requests from end users. In order to increase their revenue, web services seek for more tasks if they have the capacity and throughput. Web services can join communities to have better efficiency collabrating with others, have access to higher market share and opportunity to receive a bigger task pool from end users. The way the web services reside inside communities and how communities of web services are engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

\emph{2) Master Web Services} are responsible for managing and are representative of the communities of web services. Communities receieve tasks from users and they aim to have a healthy set of web services to perform the tasks. They seek to maximise user satisfaction by having tasks accomplished with good rate and quality. Higher user satisfaction will bring more user tasks and increase the market share of the community.

\emph{3) Users} generate tasks and try to find service providers online to perform the tasks. User satisfaction is abstracted as function of quantity and quality of tasks accomplished by our service providers.

\subsection{Web Sercive Parameters}

Web services come with different quality parameters. These parameters with a short description are listed in Table \ref{qosws}.

\begin{table}[!t]
\centering
\caption{List of web service QoS parameters.}
\begin{tabular}{|c|c||c|c|}
\hline
\textbf{Notation} & \textbf{Definition} \\
\hline\hline
$Response Time$ & The average response time of services\\
$Availability$ & Probability of available during a time frame \\
$Reliability$ & P of successfully handling tasks during a timeframe\\
$Successability$ & Probability of handling tasks successfully \\
$Throughput$ & Average rate of handling tasks \\
$Latency$ & The average latency of services\\
$Capacity$ & Amount of resources available\\
$Cost$ & Mean service fee for cooperating \\
\hline
\end{tabular}
\label{qosws}
\end{table}

We normalize and aggrigate each of these metrics to a real value between 0 and 1. Since tasks are not shared between web services and are distributed among all web serivices inside a community, one can expect tasks within a community to be performed by average quality of web service residing in that community. We use this average expected quality output, later in evaluating community $worth$ or $payoff$ function.

@@

In figure \ref{performancemany} we compare our \emph{Web Services and many Communities} scenario with a method which ignores QoS parameters and forms coalitions and allow web services to join only if they have enough requests for them in other words web services can join a community when request rate is less that throughput of all web services inside community ignoring QoS parameters. We name this method \emph{Random Formation} and use it as our benchmark for our QoS aware coalition formation process. As results illustrate clearly, our QoS aware method, forms better coalitions of web services improving performance and satisfaction for both web service and coalitions.
